```{r}
rm(list=ls())
library(readxl)
library(ggplot2)
library(Hmisc)
library(MASS)
library(caret)
library(regclass)
library(ISLR)
library(boot)
library(vcd)
library(pROC)
library (ROCR)

```

```{r}
mydata<-read_excel("Data.xlsx", sheet = 4)

colnames(mydata)[5] <- 'Age'
colnames(mydata)[6] <- 'Joined'
colnames(mydata)[7] <- 'Churned'
colnames(mydata)[8] <- 'Spend'
colnames(mydata)[1] <- 'Camp_Org'
# str(mydata)

mylogit1<-glm(Churned~Age+Joined+Spend+Camp_Org ,data=mydata,family=binomial(link="logit"))

summary(mylogit1)



#Customers who joined via campaign or organically don't signficantly influence Churn

```
```{r}
mylogit2= glm(Churned~Age+Joined+Camp_Org ,data=mydata,family=binomial(link="logit"))

summary(mylogit2)
```

```{r}
mylogit3= glm(Churned~Joined+Camp_Org ,data=mydata,family=binomial(link="logit"))

summary(mylogit3)
```

```{r}
mylogit4= glm(Churned~Camp_Org ,data=mydata,family=binomial(link="logit"))

summary(mylogit4)

# Based on all models considered, there is no significant relationship between Campaign/Organic customers and log(Odds of churn)

```

```{r}

anova(mylogit1, test="Chisq")

#As can be seen from the output, Campaign organic doesn't significantly affect the churn rate

oddsr=round(exp(cbind(OddsRatio=coef(mylogit1),confint(mylogit1))),4)

oddsr

#As the p-value for Camp_org is not significant, even though odds ratio for Camp_org is positive, we can't conclude anything.

```


```{r}
fin_model = mylogit1

preddata = data.frame(mydata)
probdefault2<-predict(fin_model,newdata=preddata,type="response")
preddefault2<-ifelse(probdefault2 > 0.5, 1,0) #at what level should we say prob(default)=1
preddata["Predicted_churn_rate"] = probdefault2
preddata["Predicted_Churn"] = preddefault2
preddata["Retention rate"] = 1-probdefault2

confMat2 = confusionMatrix(data = as.factor(preddefault2),reference = as.factor(mydata$Churned),positive = "1") #try from 0.2 #to 0.7
confMat2 ###Note, because of how this matrix is strutured, 0,0 becomes true positive -- thus we specify positive as 1


```

```{r}
roc(mydata$Churned,fin_model$fitted.values, plot=TRUE)
par(pty="s")
roc(mydata$Churned,fin_model$fitted.values, plot=TRUE, legacy.axes=TRUE, percent=TRUE, xlab="FP Rate", ylab="TP Rate",print.auc=TRUE)

#AUC of the model is only 62.7%

```

```{r}
churned_camp = data.frame(subset(preddata,preddata$Churned == 1 &  preddata$Camp_Org == 1 ))
ret_camp = data.frame(subset(preddata,preddata$Churned == 0 &  preddata$Camp_Org == 1 ))
total_camp = data.frame(subset(preddata,  preddata$Camp_Org == 1 ))

churned_org = data.frame(subset(preddata,preddata$Churned == 1 &  preddata$Camp_Org == 0 ))
ret_org = data.frame(subset(preddata,preddata$Churned ==0 &  preddata$Camp_Org == 0 ))
total_org = data.frame(subset(preddata,  preddata$Camp_Org == 0 ))

prop.test(x = c(nrow(ret_camp),nrow(ret_org)), n = c(nrow(total_camp), nrow(total_org)))

# There is no significant differnt between retention rates of customers who joined via campaign or those who joined organically

churn_rate_camp =  nrow(churned_camp)/ nrow(total_camp)
r_camp = 1 - churn_rate_camp ## retention rate of those who joined via campaign
L_camp = (1+0.1)/ (1+0.1-r_camp) ## avg expected customer life time who joined via campaign. Assume a discount factor of 0.1

churn_rate_org =  nrow(churned_org)/ nrow(total_org)
r_org = 1 - churn_rate_org ## retention rate of those who joined organically
L_org = (1+0.1)/ (1+0.1 - r_org) ## avg expected customer life time who joined organically. Assume a discount factor of 0.1


CLV_camp = (total_camp$Spend*3*0.5)*L_camp
CLV_org = (total_org$Spend*3*0.5)*L_org

t.test(CLV_camp, CLV_org, var.equal = TRUE)

#As can be seen from the t-test, there is no signficant difference between CLV values of campaign and organic customers

#m_camp = mean(total_camp$Spend*3*0.50)
# CLV_camp <- m_camp*L_camp ## CLV of customers who joined via campaign

#m_org = mean(total_org$Spend*3*0.50)
# CLV_org <- m_org*L_org ## CLV of customers who joined organically

sprintf("r_camp: %f",r_camp)
sprintf("r_org: %f",r_org)
# sprintf("CLV_camp: %f",CLV_camp)
# sprintf("CLV_org: %f",CLV_org)
```

```{r}
###### CLV for every customer 
churned = data.frame(subset(preddata, preddata$Churned == 1 ))
churn_rate = nrow(churned)/ nrow(preddata)

R_overall = 1 - churn_rate
L_overall = (1+0.1)/(1+0.1-R_overall) ## avg expected customer life time #Assume a discount factor of 0.1
# m_overall = mean(preddata$Spend*3)*0.50
# CLV_overall <- m_overall*L_overall ## CLV of customers
# CLV_overall
#sprintf("CLV overall: %f", CLV_overall)
preddata$CLV <- ((preddata$Spend*3*0.50) * L_overall)
CLV_Camp_org <- lm(preddata$CLV ~ preddata$Camp_Org+preddata$Joined+preddata$Age)
summary (CLV_Camp_org)

#Based on the model results, a customer joining via a campaign or those joining organically has no significant effect on the CLV
