title: **"LogisticReg_Default"**
output: html_notebook


Load Libraries

```{r}
rm(list=ls())
library(readxl)
library(ggplot2)
library(Hmisc)
library(MASS)
## library(caret)
library(regclass)
library(ISLR)
library(boot)
library(vcd)
library(pROC)
library (ROCR)
```


After loading the libraries, load the excel file containing data on Defaults

```{r}

##set your working directory

#setwd("/path/to/my/directory")
library("readxl")
##setwd("")
mydata = read_excel("Data2.xlsx")

summary(mydata) #summary of the data
```
You could also use

```{r}
str(mydata)
```


What do you notice? Looks like the Variables default and student are *character* and not *numeric*. Let's look at the values they take.

```{r}
head(mydata)
```

head alone might not display _all possible values_. Let's find all the possible values

```{r}
levels(as.factor(mydata$`Joined?`))
levels(as.factor(mydata$`Churned at 3 months after launch of the online community`))

```


Looks like both have only two levels and are Yes/No variables. Let's convert all No to 0 and Yes to 1. To do so, we create two new variables in the same mydata table. The two variables are labelled default2 and student2.


```{r}
mydata$churn<- ifelse(mydata$`Churned at 3 months after launch of the online community` == "No",0,1)
mydata$join <- ifelse(mydata$`Joined?` == "No",0,1)
```

Confirm the change by looking at the data again. And get the summary.

```{r}
head(mydata)

levels(as.factor(mydata$churn))
levels(as.factor(mydata$join)) #if you wanted to recheck the levels
```
```{r}
summary(mydata)
```

Looks like it worked!

Now let's code the model. We want to predict default. The independent variables in our dataset are 'student=Yes/No', 'balance' and 'income'. The default variable is discrete and has only two levels: {0,1}. Unlike in a regression, where the dependent variable is continuous, default being discrete does not lend itself to standard regression analysis.

```{r}
#Logistic Regression Model Estimation
mylogit<-glm(`Churned at 3 months after launch of the online community`~ `Average Spend Last 3 months of Life with the firm`+ `Joined?`+ `Customer Age with Firm at time of launching the online community` ,data=mydata,family=binomial(link="logit"))
```


Let's output the results

```{r}
#coefficients
summary(mylogit)
```

While the p-values indicate confidence, we could also output the 2.5% and 97.5% confindence intervals
```{r}
#Confidence Intervals
Confidence=confint(mylogit) 
Confidence
```

Another way to interpret the parameter estimates would be to compute the Odds Ratios

```{r}
#Odds Ratio Calculation, including confidence intervals
oddsr=round(exp(cbind(OddsRatio=coef(mylogit),confint(mylogit))),4)

oddsr

##CLV Calculation 
## we calculate L -> the xepected lifetime of a consumer 
churn_yes_joined <- data.frame(subset(mydata, mydata$`Churned at 3 months after launch of the online community`== 1 &  mydata$`Joined?`== 1 ))


churn_total_joined <- data.frame(subset(mydata,  mydata$`Joined?`== 1 ))



nr <-nrow(churn_yes_joined)
dr <- nrow(churn_total_joined)
churn_of_those_who_joined <- nr/ dr

churn_of_those_who_joined

r <- 1- churn_of_those_who_joined ## retention rate of those who joined
r
L <- 1/ (1-r) ## avg expected customer life time 
m <- mean(churn_total_joined$Average.Spend.Last.3.months.of.Life.with.the.firm*3)*0.50
CLV <- m*L ## CLV of customers who joined 
CLV 

churn_yes_not_joined <- data.frame(subset(mydata, mydata$`Churned at 3 months after launch of the online community`== 1 &  mydata$`Joined?`== 0 ))


churn_total_not_joined <- data.frame(subset(mydata,  mydata$`Joined?`== 0 ))

nr_nj <-nrow(churn_yes_not_joined)
dr_nj <- nrow(churn_total_not_joined)
churn_of_those_who_didnt_join <- nr_nj/ dr_nj

churn_of_those_who_didnt_join
r_nj <- 1- churn_of_those_who_didnt_join ## retention rate of those who joined
L_nj <- 1/ (1-r_nj) ## avg expected customer life time 
m_nj <- mean(churn_total_not_joined$Average.Spend.Last.3.months.of.Life.with.the.firm*3) *0.50
CLV_nj <- m_nj*L_nj ## CLV of customers who joined 

CLV_nj

r_nj

###### CLV forevery customer 
churn_yes <- data.frame(subset(mydata, mydata$`Churned at 3 months after launch of the online community`== 1 ))
churn <- nrow(churn_yes)/ nrow(mydata)

R <- 1 - churn
L <- 1/(1-R)


mydata$CLV <- ((mydata$`Average Spend Last 3 months of Life with the firm`*0.50) * L)

CLV_Joined <- lm(mydata$CLV ~ mydata$`Joined?`)
summary (CLV_Joined)
```
